Supermassive black hole and host spheroid affairs \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram

### 2015-08-21 papers/MbhMsph/mm.tex
vaffanculo e venerdi

\begin{table*}
\centering
\caption{Linear regression analysis of the $M_{\rm BH} - L_{\rm gal}$ diagram.}
\begin{tabular}{llccccc}
\tableline\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle MAG_{\rm gal} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - \langle MAG_{\rm gal} \rangle)/{\rm mag}]$} \\ [0.5em]
 All (62)               & BCES $(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
                        & mFITEXY $(Y|X)$  & $8.26^{+0.08}_{-0.08}$ & $-0.49^{+0.06}_{-0.07}$ & $-24.78$ & $0.61^{+0.07}_{-0.06}$ & $0.64$ \\
                        & {\tt linmix\_err} $(Y|X)$  & $8.26 \pm 0.09$ & $-0.49 \pm 0.07$ & $-24.78$ & $0.63 \pm 0.07$ & $0.64$ \\ [0.5em]
                        & BCES $(X|Y)$   & $8.26 \pm 0.12$ & $-1.01 \pm 0.15$ & $-24.78$ & $-$ & $0.92$ \\
                        & mFITEXY $(X|Y)$  & $8.26^{+0.11}_{-0.12}$ & $-1.03^{+0.13}_{-0.16}$ & $-24.78$ & $0.88^{+0.10}_{-0.08}$ & $0.93$ \\
                        & {\tt linmix\_err} $(X|Y)$  & $8.26 \pm 0.12$ & $-1.02 \pm 0.15$ & $-24.78$ & $0.91 \pm 0.17$ & $0.93$ \\ [0.5em]
                        & BCES Bisector  & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
                        & mFITEXY Bisector & $8.26^{+0.10}_{-0.10}$ & $-0.73^{+0.09}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
                        & {\tt linmix\_err} Bisector & $8.26 \pm 0.10$ & $-0.72 \pm 0.15$ & $-24.78$ & $-$    & $0.71$ \\ [0.5em]

 Early-type (E+S0) (45) & BCES $(Y|X)$   & $8.56 \pm 0.07$ & $-0.44 \pm 0.05$ & $-24.88$ & $-$ & $0.45$ \\
                        & mFITEXY $(Y|X)$  & $8.56^{+0.06}_{-0.06}$ & $-0.42^{+0.05}_{-0.05}$ & $-24.88$ & $0.41^{+0.06}_{-0.05}$ & $0.45$ \\
                        & {\tt linmix\_err} $(Y|X)$  & $8.56 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.88$ & $0.43 \pm 0.06$ & $0.45$ \\ [0.5em]
                        & BCES $(X|Y)$   & $8.56 \pm 0.08$ & $-0.64 \pm 0.05$ & $-24.88$ & $-$ & $0.53$ \\
                        & mFITEXY $(X|Y)$  & $8.56^{+0.08}_{-0.08}$ & $-0.66^{+0.07}_{-0.08}$ & $-24.88$ & $0.51^{+0.07}_{-0.06}$ & $0.55$ \\
                        & {\tt linmix\_err} $(X|Y)$  & $8.56 \pm 0.09$ & $-0.65 \pm 0.08$ & $-24.88$ & $0.53 \pm 0.10$ & $0.54$ \\ [0.5em]
                        & BCES Bisector  & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $-24.88$ & $-$ & $0.47$ \\
                        & mFITEXY Bisector & $8.56^{+0.07}_{-0.07}$ & $-0.54^{+0.06}_{-0.06}$ & $-24.88$ & $-$    & $0.47$ \\
                        & {\tt linmix\_err} Bisector & $8.56 \pm 0.08$ & $-0.53 \pm 0.10$ & $-24.88$ & $-$    & $0.47$ \\ [0.5em]

@@

\begin{table*}
\centering
\caption{Linear regression analysis of the $M_{\rm BH} - L_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle MAG_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
 & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - \langle MAG_{\rm sph} \rangle)/{\rm mag}]$} \\ [0.5em]
All (66)               & BCES $(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
                       & mFITEXY $(Y|X)$    & $8.17^{+0.06}_{-0.07}$ & $-0.43^{+0.03}_{-0.04}$ & $-23.86$ & $0.49^{+0.06}_{-0.05}$ & $0.56$ \\
                       & {\tt linmix\_err} $(Y|X)$     & $8.16 \pm 0.07$ & $-0.42 \pm 0.04$ & $-23.86$ & $0.51 \pm 0.06$ & $0.56$ \\ [0.5em]
                       & BCES $(X|Y)$   & $8.16 \pm 0.08$ & $-0.61 \pm 0.05$ & $-23.86$ & $-$ & $0.68$ \\
                       & mFITEXY $(X|Y)$    & $8.15^{+0.07}_{-0.08}$ & $-0.61^{+0.05}_{-0.05}$ & $-23.86$ & $0.58^{+0.07}_{-0.06}$ & $0.68$ \\
                       & {\tt linmix\_err} $(X|Y)$     & $8.16 \pm 0.09$ & $-0.60 \pm 0.06$ & $-23.86$ & $0.60 \pm 0.09$ & $0.67$ \\ [0.5em]
                       & BCES Bisector  & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
                       & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\
                       & {\tt linmix\_err} Bisector    & $8.16 \pm 0.08$ & $-0.51 \pm 0.09$ & $-23.86$ & $-$    & $0.59$ \\ [0.5em]

$n>2$ (43)             & BCES $(Y|X)$      & $8.58 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.77$ & $-$ & $0.46$ \\
                       & mFITEXY $(Y|X)$    & $8.57^{+0.07}_{-0.06}$ & $-0.41^{+0.04}_{-0.04}$ & $-24.77$ & $0.38^{+0.06}_{-0.06}$ & $0.46$ \\
                       & {\tt linmix\_err} $(Y|X)$     & $8.56 \pm 0.07$ & $-0.39 \pm 0.05$ & $-24.77$ & $0.40 \pm 0.06$ & $0.46$ \\ [0.5em]
                       & BCES $(X|Y)$      & $8.58 \pm 0.08$ & $-0.58 \pm 0.06$ & $-24.77$ & $-$ & $0.56$ \\
                       & mFITEXY $(X|Y)$    & $8.56^{+0.08}_{-0.08}$ & $-0.57^{+0.06}_{-0.07}$ & $-24.77$ & $0.44^{+0.08}_{-0.11}$ & $0.55$ \\
                       & {\tt linmix\_err} $(X|Y)$     & $8.55 \pm 0.09$ & $-0.57 \pm 0.08$ & $-24.77$ & $0.49 \pm 0.10$ & $0.55$ \\ [0.5em]
                       & BCES Bisector     & $8.58 \pm 0.07$ & $-0.50 \pm 0.05$ & $-24.77$ & $-$ & $0.49$ \\
                       & mFITEXY Bisector   & $8.57^{+0.07}_{-0.07}$ & $-0.49^{+0.05}_{-0.05}$ & $-24.77$ & $-$    & $0.49$ \\
                       & {\tt linmix\_err} Bisector    & $8.56 \pm 0.08$ & $-0.48 \pm 0.10$ & $-24.77$ & $-$    & $0.49$ \\  [0.5em]

Core-S\'ersic (22) & BCES $(Y|X)$   & $9.06 \pm 0.09$ & $-0.32 \pm 0.11$  & $-25.73$ & $-$    & $0.42$ \\
                   & mFITEXY $(Y|X)$   & $9.06^{+0.08}_{-0.09}$ & $-0.26^{+0.08}_{-0.07}$ & $-25.73$ & $0.36^{+0.09}_{-0.06}$ & $0.42$ \\
                   & {\tt linmix\_err} $(Y|X)$  & $9.04 \pm 0.10$ & $-0.24 \pm 0.09$ & $-25.73$ & $0.40 \pm 0.08$ & $0.42$ \\ [0.5em]
                   & BCES $(X|Y)$   & $9.06 \pm 0.12$ & $-0.65 \pm 0.12$  & $-25.73$ & $-$    & $0.61$ \\
                   & mFITEXY $(X|Y)$   & $9.03^{+0.15}_{-0.16}$ & $-0.72^{+0.17}_{-0.31}$ & $-25.73$ & $0.61^{+0.14}_{-0.09}$ & $0.68$ \\
                   & {\tt linmix\_err} $(X|Y)$  & $9.03 \pm 0.17$ & $-0.69 \pm 0.27$ & $-25.73$ & $0.68 \pm 0.30$ & $0.64$ \\ [0.5em]
                   & BCES Bisector  & $9.06 \pm 0.10$ & $-0.47 \pm 0.08$  & $-25.73$ & $-$    & $0.48$ \\
                   & mFITEXY Bisector  & $9.05^{+0.12}_{-0.13}$ & $-0.47^{+0.12}_{-0.17}$ & $-25.73$ & $-$    & $0.48$ \\
                   & {\tt linmix\_err} Bisector & $9.04 \pm 0.14$ & $-0.44 \pm 0.16$ & $-25.73$ & $-$    & $0.46$ \\ [0.5em]

S\'ersic (44) & BCES $(Y|X)$   & $7.71 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $-$    & $0.61$ \\
              & mFITEXY $(Y|X)$   & $7.72^{+0.08}_{-0.09}$ & $-0.41^{+0.07}_{-0.08}$ & $-22.92$ & $0.54^{+0.08}_{-0.07}$ & $0.61$ \\
              & {\tt linmix\_err} $(Y|X)$  & $7.73 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $0.55 \pm 0.08$ & $0.61$ \\ [0.5em]
              & BCES $(X|Y)$   & $7.71 \pm 0.14$ & $-0.86 \pm 0.16$ & $-22.92$ & $-$    & $0.93$ \\
              & mFITEXY $(X|Y)$   & $7.72^{+0.14}_{-0.13}$ & $-0.86^{+0.13}_{-0.19}$ & $-22.92$ & $0.77^{+0.13}_{-0.10}$ & $0.93$ \\
              & {\tt linmix\_err} $(X|Y)$  & $7.73 \pm 0.14$ & $-0.86 \pm 0.17$ & $-22.92$ & $0.79 \pm  0.20$ & $0.93$ \\ [0.5em]
              & BCES Bisector  & $7.71 \pm 0.10$  & $-0.61 \pm 0.08$ & $-22.92$ & $-$    & $0.71$ \\
              & mFITEXY Bisector  & $7.72^{+0.11}_{-0.11}$ & $-0.61^{+0.10}_{-0.12}$ & $-22.92$ & $-$                    & $0.71$ \\
              & {\tt linmix\_err} Bisector & $7.73 \pm 0.12$ & $-0.62 \pm 0.15$ & $-22.92$ & $-$    & $0.71$ \\ [0.5em]

@@

{\bf Early-type (E+S0)} (45) & BCES $(Y|X)$    & $8.56 \pm 0.07$ & $-0.33 \pm 0.04$ & $-24.47$ & $-$    & $0.46$ \\
                             & mFITEXY $(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40^{+0.06}_{-0.05}$ & $0.46$ \\
                             & {\tt linmix\_err} $(Y|X)$  & $8.55 \pm 0.07$ & $-0.32 \pm 0.04$ & $-24.47$ & $0.41 \pm 0.06$ & $0.46$ \\ [0.5em]
                             & BCES $(X|Y)$    & $8.56 \pm 0.08$ & $-0.48 \pm 0.05$ & $-24.47$ & $-$    & $0.55$ \\
                             & mFITEXY $(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $0.49^{+0.08}_{-0.06}$ & $0.57$\\
                             & {\tt linmix\_err} $(X|Y)$  & $8.55 \pm 0.09$ & $-0.48 \pm 0.06$ & $-24.47$ & $0.51 \pm 0.10$ & $0.56$ \\ [0.5em]
                             & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{-0.40 \pm 0.04}$ & $\boldsymbol{-24.47}$ & $-$    & $\boldsymbol{0.49}$ \\
                             & mFITEXY Bisector   & $8.55^{+0.07}_{-0.07}$ & $-0.41^{+0.04}_{-0.05}$ & $-24.47$ & $-$    & $0.49$ \\
                             & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $-0.40 \pm 0.09$ & $-24.47$ & $-$    & $0.49$ \\ [0.5em]

{\bf Late-type (Sp)} (17) & BCES $(Y|X)$    & $7.18 \pm 0.16$ & $-0.79 \pm 0.43$ & $-22.33$ & $-$    & $0.70$ \\
                          & mFITEXY $(Y|X)$    & $7.20^{+0.15}_{-0.15}$ & $-0.53^{+0.22}_{-0.24}$ & $-22.33$ & $0.55^{+0.15}_{-0.10}$ & $0.63$ \\
                          & {\tt linmix\_err} $(Y|X)$  & $7.24 \pm 0.19$ & $-0.46 \pm 0.32$ & $-22.33$ & $0.63 \pm 0.16$ & $0.62$ \\ [0.5em]
                          & BCES $(X|Y)$    & $7.18 \pm 0.29$ & $-1.71 \pm 0.71$ & $-22.33$ & $-$    & $1.26$ \\
                          & mFITEXY $(X|Y)$    & $7.38^{+0.54}_{-0.36}$ & $-2.02^{+0.71}_{-2.13}$ & $-22.33$ & $1.09^{+0.41}_{-0.24}$ & $1.50$ \\
                          & {\tt linmix\_err} $(X|Y)$  & $7.34 \pm 0.43$ & $-1.93 \pm 1.30$ & $-22.33$ & $1.31 \pm 0.97$ & $1.43$ \\ [0.5em]
                          & {\bf BCES Bisector}& $\boldsymbol{7.18 \pm 0.20}$ & $\boldsymbol{-1.15 \pm 0.27}$ & $\boldsymbol{-22.33}$ & $-$    & $\boldsymbol{0.88}$ \\
                          & mFITEXY Bisector   & $7.26^{+0.40}_{-0.28}$ & $-1.03^{+0.33}_{-0.52}$ & $-22.33$ & $-$    & $0.82$ \\
                          & {\tt linmix\_err} Bisector & $7.27 \pm 0.33$ & $-0.96 \pm 0.50$ & $-22.33$ & $-$    & $0.78$ \\ [0.5em]

>>>>

\begin{table*}
\centering
\caption{Linear regression analysis of the $M_{\rm BH} - L_{\rm gal}$ diagram.}
\begin{tabular}{llccccc}
\tableline\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle MAG_{\rm gal} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - \langle MAG_{\rm gal} \rangle)/{\rm mag}]$} \\ [0.5em]
 All (62)               & BCES $(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
                        & mFITEXY $(Y|X)$  & $8.26^{+0.08}_{-0.08}$ & $-0.49^{+0.06}_{-0.07}$ & $-24.78$ & $0.61^{+0.07}_{-0.06}$ & $0.64$ \\
                        & {\tt linmix\_err} $(Y|X)$  & $8.26 \pm 0.09$ & $-0.49 \pm 0.07$ & $-24.78$ & $0.63 \pm 0.07$ & $0.64$ \\ [0.5em]
                        & BCES $(X|Y)$   & $8.26 \pm 0.12$ & $-1.01 \pm 0.15$ & $-24.78$ & $-$ & $0.92$ \\
                        & mFITEXY $(X|Y)$  & $8.26^{+0.11}_{-0.12}$ & $-1.03^{+0.13}_{-0.16}$ & $-24.78$ & $0.88^{+0.10}_{-0.08}$ & $0.93$ \\
                        & {\tt linmix\_err} $(X|Y)$  & $8.26 \pm 0.12$ & $-1.02 \pm 0.15$ & $-24.78$ & $0.91 \pm 0.17$ & $0.93$ \\ [0.5em]
                        & BCES Bisector  & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
                        & mFITEXY Bisector & $8.26^{+0.10}_{-0.10}$ & $-0.73^{+0.09}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
                        & {\tt linmix\_err} Bisector & $8.26 \pm 0.10$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$    & $0.71$ \\ [0.5em]

 Early-type (E+S0) (45) & BCES $(Y|X)$   & $8.56 \pm 0.07$ & $-0.44 \pm 0.05$ & $-24.88$ & $-$ & $0.45$ \\
                        & mFITEXY $(Y|X)$  & $8.56^{+0.06}_{-0.06}$ & $-0.42^{+0.05}_{-0.05}$ & $-24.88$ & $0.41^{+0.06}_{-0.05}$ & $0.45$ \\
                        & {\tt linmix\_err} $(Y|X)$  & $8.56 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.88$ & $0.43 \pm 0.06$ & $0.45$ \\ [0.5em]
                        & BCES $(X|Y)$   & $8.56 \pm 0.08$ & $-0.64 \pm 0.05$ & $-24.88$ & $-$ & $0.53$ \\
                        & mFITEXY $(X|Y)$  & $8.56^{+0.08}_{-0.08}$ & $-0.66^{+0.07}_{-0.08}$ & $-24.88$ & $0.51^{+0.07}_{-0.06}$ & $0.55$ \\
                        & {\tt linmix\_err} $(X|Y)$  & $8.56 \pm 0.09$ & $-0.65 \pm 0.08$ & $-24.88$ & $0.53 \pm 0.10$ & $0.54$ \\ [0.5em]
                        & BCES Bisector  & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $-24.88$ & $-$ & $0.47$ \\
                        & mFITEXY Bisector & $8.56^{+0.07}_{-0.07}$ & $-0.54^{+0.06}_{-0.06}$ & $-24.88$ & $-$    & $0.47$ \\
                        & {\tt linmix\_err} Bisector & $8.56 \pm 0.08$ & $-0.53 \pm 0.05$ & $-24.88$ & $-$    & $0.47$ \\ [0.5em]

@@

\begin{table*}
\centering
\caption{Linear regression analysis of the $M_{\rm BH} - L_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle MAG_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
 & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - \langle MAG_{\rm sph} \rangle)/{\rm mag}]$} \\ [0.5em]
All (66)               & BCES $(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
                       & mFITEXY $(Y|X)$    & $8.17^{+0.06}_{-0.07}$ & $-0.43^{+0.03}_{-0.04}$ & $-23.86$ & $0.49^{+0.06}_{-0.05}$ & $0.56$ \\
                       & {\tt linmix\_err} $(Y|X)$     & $8.16 \pm 0.07$ & $-0.42 \pm 0.04$ & $-23.86$ & $0.51 \pm 0.06$ & $0.56$ \\ [0.5em]
                       & BCES $(X|Y)$   & $8.16 \pm 0.08$ & $-0.61 \pm 0.05$ & $-23.86$ & $-$ & $0.68$ \\
                       & mFITEXY $(X|Y)$    & $8.15^{+0.07}_{-0.08}$ & $-0.61^{+0.05}_{-0.05}$ & $-23.86$ & $0.58^{+0.07}_{-0.06}$ & $0.68$ \\
                       & {\tt linmix\_err} $(X|Y)$     & $8.16 \pm 0.09$ & $-0.60 \pm 0.06$ & $-23.86$ & $0.60 \pm 0.09$ & $0.67$ \\ [0.5em]
                       & BCES Bisector  & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
                       & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\
                       & {\tt linmix\_err} Bisector    & $8.16 \pm 0.08$ & $-0.51 \pm 0.03$ & $-23.86$ & $-$    & $0.59$ \\ [0.5em]

$n>2$ (43)             & BCES $(Y|X)$      & $8.58 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.77$ & $-$ & $0.46$ \\
                       & mFITEXY $(Y|X)$    & $8.57^{+0.07}_{-0.06}$ & $-0.41^{+0.04}_{-0.04}$ & $-24.77$ & $0.38^{+0.06}_{-0.06}$ & $0.46$ \\
                       & {\tt linmix\_err} $(Y|X)$     & $8.56 \pm 0.07$ & $-0.39 \pm 0.05$ & $-24.77$ & $0.40 \pm 0.06$ & $0.46$ \\ [0.5em]
                       & BCES $(X|Y)$      & $8.58 \pm 0.08$ & $-0.58 \pm 0.06$ & $-24.77$ & $-$ & $0.56$ \\
                       & mFITEXY $(X|Y)$    & $8.56^{+0.08}_{-0.08}$ & $-0.57^{+0.06}_{-0.07}$ & $-24.77$ & $0.44^{+0.08}_{-0.11}$ & $0.55$ \\
                       & {\tt linmix\_err} $(X|Y)$     & $8.55 \pm 0.09$ & $-0.57 \pm 0.08$ & $-24.77$ & $0.49 \pm 0.10$ & $0.55$ \\ [0.5em]
                       & BCES Bisector     & $8.58 \pm 0.07$ & $-0.50 \pm 0.05$ & $-24.77$ & $-$ & $0.49$ \\
                       & mFITEXY Bisector   & $8.57^{+0.07}_{-0.07}$ & $-0.49^{+0.05}_{-0.05}$ & $-24.77$ & $-$    & $0.49$ \\
                       & {\tt linmix\_err} Bisector    & $8.56 \pm 0.08$ & $-0.48 \pm 0.05$ & $-24.77$ & $-$    & $0.49$ \\  [0.5em]

Core-S\'ersic (22) & BCES $(Y|X)$   & $9.06 \pm 0.09$ & $-0.32 \pm 0.11$  & $-25.73$ & $-$    & $0.42$ \\
                   & mFITEXY $(Y|X)$   & $9.06^{+0.08}_{-0.09}$ & $-0.26^{+0.08}_{-0.07}$ & $-25.73$ & $0.36^{+0.09}_{-0.06}$ & $0.42$ \\
                   & {\tt linmix\_err} $(Y|X)$  & $9.04 \pm 0.10$ & $-0.24 \pm 0.09$ & $-25.73$ & $0.40 \pm 0.08$ & $0.42$ \\ [0.5em]
                   & BCES $(X|Y)$   & $9.06 \pm 0.12$ & $-0.65 \pm 0.12$  & $-25.73$ & $-$    & $0.61$ \\
                   & mFITEXY $(X|Y)$   & $9.03^{+0.15}_{-0.16}$ & $-0.72^{+0.17}_{-0.31}$ & $-25.73$ & $0.61^{+0.14}_{-0.09}$ & $0.68$ \\
                   & {\tt linmix\_err} $(X|Y)$  & $9.03 \pm 0.17$ & $-0.69 \pm 0.27$ & $-25.73$ & $0.68 \pm 0.30$ & $0.64$ \\ [0.5em]
                   & BCES Bisector  & $9.06 \pm 0.10$ & $-0.47 \pm 0.08$  & $-25.73$ & $-$    & $0.48$ \\
                   & mFITEXY Bisector  & $9.05^{+0.12}_{-0.13}$ & $-0.47^{+0.12}_{-0.17}$ & $-25.73$ & $-$    & $0.48$ \\
                   & {\tt linmix\_err} Bisector & $9.04 \pm 0.14$ & $-0.44 \pm 0.12$ & $-25.73$ & $-$    & $0.46$ \\ [0.5em]

S\'ersic (44) & BCES $(Y|X)$   & $7.71 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $-$    & $0.61$ \\
              & mFITEXY $(Y|X)$   & $7.72^{+0.08}_{-0.09}$ & $-0.41^{+0.07}_{-0.08}$ & $-22.92$ & $0.54^{+0.08}_{-0.07}$ & $0.61$ \\
              & {\tt linmix\_err} $(Y|X)$  & $7.73 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $0.55 \pm 0.08$ & $0.61$ \\ [0.5em]
              & BCES $(X|Y)$   & $7.71 \pm 0.14$ & $-0.86 \pm 0.16$ & $-22.92$ & $-$    & $0.93$ \\
              & mFITEXY $(X|Y)$   & $7.72^{+0.14}_{-0.13}$ & $-0.86^{+0.13}_{-0.19}$ & $-22.92$ & $0.77^{+0.13}_{-0.10}$ & $0.93$ \\
              & {\tt linmix\_err} $(X|Y)$  & $7.73 \pm 0.14$ & $-0.86 \pm 0.17$ & $-22.92$ & $0.79 \pm  0.20$ & $0.93$ \\ [0.5em]
              & BCES Bisector  & $7.71 \pm 0.10$  & $-0.61 \pm 0.08$ & $-22.92$ & $-$    & $0.71$ \\
              & mFITEXY Bisector  & $7.72^{+0.11}_{-0.11}$ & $-0.61^{+0.10}_{-0.12}$ & $-22.92$ & $-$                    & $0.71$ \\
              & {\tt linmix\_err} Bisector & $7.73 \pm 0.12$ & $-0.62 \pm 0.09$ & $-22.92$ & $-$    & $0.71$ \\ [0.5em]

@@

{\bf Early-type (E+S0)} (45) & BCES $(Y|X)$    & $8.56 \pm 0.07$ & $-0.33 \pm 0.04$ & $-24.47$ & $-$    & $0.46$ \\
                             & mFITEXY $(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40^{+0.06}_{-0.05}$ & $0.46$ \\
                             & {\tt linmix\_err} $(Y|X)$  & $8.55 \pm 0.07$ & $-0.32 \pm 0.04$ & $-24.47$ & $0.41 \pm 0.06$ & $0.46$ \\ [0.5em]
                             & BCES $(X|Y)$    & $8.56 \pm 0.08$ & $-0.48 \pm 0.05$ & $-24.47$ & $-$    & $0.55$ \\
                             & mFITEXY $(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $0.49^{+0.08}_{-0.06}$ & $0.57$\\
                             & {\tt linmix\_err} $(X|Y)$  & $8.55 \pm 0.09$ & $-0.48 \pm 0.06$ & $-24.47$ & $0.51 \pm 0.10$ & $0.56$ \\ [0.5em]
                             & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{-0.40 \pm 0.04}$ & $\boldsymbol{-24.47}$ & $-$    & $\boldsymbol{0.49}$ \\
                             & mFITEXY Bisector   & $8.55^{+0.07}_{-0.07}$ & $-0.41^{+0.04}_{-0.05}$ & $-24.47$ & $-$    & $0.49$ \\
                             & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $-0.40 \pm 0.04$ & $-24.47$ & $-$    & $0.49$ \\ [0.5em]

{\bf Late-type (Sp)} (17) & BCES $(Y|X)$    & $7.18 \pm 0.16$ & $-0.79 \pm 0.43$ & $-22.33$ & $-$    & $0.70$ \\
                          & mFITEXY $(Y|X)$    & $7.20^{+0.15}_{-0.15}$ & $-0.53^{+0.22}_{-0.24}$ & $-22.33$ & $0.55^{+0.15}_{-0.10}$ & $0.63$ \\
                          & {\tt linmix\_err} $(Y|X)$  & $7.24 \pm 0.19$ & $-0.46 \pm 0.32$ & $-22.33$ & $0.63 \pm 0.16$ & $0.62$ \\ [0.5em]
                          & BCES $(X|Y)$    & $7.18 \pm 0.29$ & $-1.71 \pm 0.71$ & $-22.33$ & $-$    & $1.26$ \\
                          & mFITEXY $(X|Y)$    & $7.38^{+0.54}_{-0.36}$ & $-2.02^{+0.71}_{-2.13}$ & $-22.33$ & $1.09^{+0.41}_{-0.24}$ & $1.50$ \\
                          & {\tt linmix\_err} $(X|Y)$  & $7.34 \pm 0.43$ & $-1.93 \pm 1.30$ & $-22.33$ & $1.31 \pm 0.97$ & $1.43$ \\ [0.5em]
                          & {\bf BCES Bisector}& $\boldsymbol{7.18 \pm 0.20}$ & $\boldsymbol{-1.15 \pm 0.27}$ & $\boldsymbol{-22.33}$ & $-$    & $\boldsymbol{0.88}$ \\
                          & mFITEXY Bisector   & $7.26^{+0.40}_{-0.28}$ & $-1.03^{+0.33}_{-0.52}$ & $-22.33$ & $-$    & $0.82$ \\
                          & {\tt linmix\_err} Bisector & $7.27 \pm 0.33$ & $-0.96 \pm 0.37$ & $-22.33$ & $-$    & $0.78$ \\ [0.5em]
